---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)

sales <- read_csv("sales.csv")
sales %>% head()

```

- `X1` seems to be a useless identifier, can remove.
- Various event identifiers don't help us much, can remove.
- Plenty of missing values.
- Plenty of date columns. 

Will look at the stucture of the data and understand the missing values.

```{r}
glimpse(sales)

```
The date columns have a mix of data types, some are date, date-time or chars. 

Let's count the missing values per column.

```{r}
sales %>%
  lapply(is.na) %>%
  sapply(sum)

```

The last 14 columns are almost entirely missing values, so we'll remove them. Also the `web_session_cookie_val` column doesn't provide much use, we'll remove it too.

```{r}

sales2 <- sales %>%
  select(event_name:fin_mkt_nm)

```


```{r}
glimpse(sales2)
```

Let's clean up the dates and date-times. I'll split the dttm fields into a date and time. Then will ensure all date and time fields have the correct type. 

```{r}
sales3 <- separate(sales2, event_date_time,
                   c("event_dt", "event_time"), sep = " ")

sales4 <- separate(sales3, sales_ord_create_dttm,
                   c("ord_create_dt", "ord_create_time"), sep = " ")

```

```{r}
glimpse(sales4)
```

All the date fields end in `dt`, all the time fields now end in `time`. Let's exploit this to change their type.

```{r}
date_cols <- str_detect(names(sales4), "dt")
time_cols <- c("event_time", "ord_create_time")

library(lubridate)
sales4[, date_cols] <- lapply(sales4[, date_cols], ymd)
sales4[, time_cols] <- lapply(sales4[, time_cols], hms)
glimpse(sales4)
```

```{r}
head(sales4$ord_create_time)
```

I noticed that some fields have NULL, some have NA for missing values. Let's check both and decide how to we can resolve these.

```{r}
sales4[, str_detect(sales4, "NULL")]
```

```{r}

sales4$secondary_act_name <- str_replace(sales4$secondary_act_name, "NULL", "None")
sales4$sales_platform_cd <- str_replace(sales4$sales_platform_cd, "NULL", "None")

```


